The Holy Hand Grenade of Antioch

### 2020-02-22 draft-camelot-holy-grenade.tex
fix: sections depth
fix: asides and comments

%% Temporary fixes %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newenvironment{aside}{}{}
\newenvironment{comment}{}{}
\let\cmt\relax% [comment]#...#
\let\bcp\relax% [bcp14]#...#
\usepackage{verbatim}
\newenvironment{sourcecode}{\verbatim}{\endverbatim}
\usepackage{longtable}
\usepackage{multirow}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% [toc=exclude]
% :sectnums!:
\subsection{Terminology}

@@

:sectnums:
\subsection{Introduction}

@@

\subsection{The French-occupied castle}

@@

% TODO PB: aside environment
\begin{aside}
  While the exchange at the French-occupied castle is one of
  the more memorable scenes of 
  \textbf{Monty Python and the Holy Grail},
  the Trojan Rabbit has not reached the same level of cultural
  resonance as its more murderous counterpart. Reasons for this
  may include:

  \begin{itemize}
    \item Less overall screen-time dedicated to the Trojan Rabbit.
    \item The Trojan Rabbit as projectile has already been anticipated
    by the Cow as projectile.
  \end{itemize}
\end{aside}

@@

% TODO: is this a comment?
\begin{comment}
  TODO: Will need to verify that claim.
\end{comment}

% TODO: is this a comment?
\begin{comment}
  Strictly speaking, the Knights are Welsh.
\end{comment}

% TODO: this is a comment, but how should it be formatted?
\begin{comment}
This document, as it turns out, has a profusion of XML comments.

@@

\subsection{The Mythos of Caerbannog}
\label{caerbannog}

@@

\subsubsection{The Killer Rabbit of Caerbannog}
\label{killer_rabbit_caerbannog}
% TODO: this label ain't behaving -- why?

@@

\subsubsection{Holy Hand Grenade of Antioch}
\label{holy_hand_grenade}

@@

\subsection{Dramatis Personae}

@@

\subsubsection{Past the Killer Rabbit}

@@

\subsection{IANA Considerations}

@@

\subsection{Security Considerations}

>>>>

%% Temporary fixes %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\let\bcp\relax% [bcp14]#...#

\usepackage{verbatim}
\newenvironment{sourcecode}{\verbatim}{\endverbatim}

\usepackage{longtable}
\usepackage{multirow}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% [toc=exclude]
% :sectnums!:
\section{Terminology}

@@

:sectnums:
\section{Introduction}

@@

\section{The French-occupied castle}

@@

\begin{reviewernote}
  While the exchange at the French-occupied castle is one of
  the more memorable scenes of 
  \textbf{Monty Python and the Holy Grail},
  the Trojan Rabbit has not reached the same level of cultural
  resonance as its more murderous counterpart. Reasons for this
  may include:

  \begin{itemize}
    \item Less overall screen-time dedicated to the Trojan Rabbit.
    \item The Trojan Rabbit as projectile has already been anticipated
    by the Cow as projectile.
  \end{itemize}
\end{reviewernote}

@@

\begin{reviewernote}
  TODO: Will need to verify that claim.
\end{reviewernote}

\begin{reviewernote}
  Strictly speaking, the Knights are Welsh.
\end{reviewernote}

\begin{comment}
This document, as it turns out, has a profusion of XML comments.

@@

\section{The Mythos of Caerbannog}
\label{caerbannog}

@@

\subsection{The Killer Rabbit of Caerbannog}
\label{killer_rabbit_caerbannog}
% TODO: this label ain't behaving -- why?

@@

\subsection{Holy Hand Grenade of Antioch}
\label{holy_hand_grenade}

@@

\section{Dramatis Personae}

@@

\subsection{Past the Killer Rabbit}

@@

\section{IANA Considerations}

@@

\section{Security Considerations}
